Urbanization and Public Transportation of Los Angeles

### 2023-11-27 Paper.Rmd
Update Paper.Rmd

>>>>

This information is crucial for making impactful decisions related to resource allocation, service expansion, and policy adjustments. Transit agencies can use this information to optimize fare structures, implement dynamic pricing models, or introduce discounts and incentives to attract more riders during specific times or for particular modes. Additionally, knowing how pricing, availability, and convenience impact ridership allows for targeted marketing and communication strategies.
